# Metric smacof

In this part of the manual we discuss metric MDS, and the program
smacofME. Metric MDS is the core of all smacof programs, because they
all have the majorization algorithm based on the Guttman transform 
in common.

## Program

### Parameters

```{r parameters, eval = FALSE}
smacofME <- function(thedata,
                     ndim = 2,
                     xold = NULL,
                     labels = NULL,
                     width = 15,
                     precision = 10,
                     itmax = 1000,
                     eps = 1e-10,
                     verbose = TRUE,
                     jitmax = 20,
                     jeps = 1e-10,
                     jverbose = FALSE,
                     kitmax = 20,
                     keps = 1e-10,
                     kverbose = FALSE,
                     init = 1)
```

Parameter *ndim* is the number of dimensions, and *init* tells if an initial configuration
is read from a file (init = 1), is computed using classical scaling (init = 2), or is
a random configuration (init = 3). Parameters
*itmax*, *epsi*, and *verbose* control the iterations. The maximum number of iterations
is *itmax*, the iterations stop if the decrease of stress in an iteration is less than
1E-*epsi*, and if *verbose* is one intermediate iteration results are written to stdout.
These intermediate iteration results are formatted with the R function formatC(), using
*width* for the width argument and *precision* for the digits argument. 

## Algorithm




## Output

```{r output, eval = FALSE}
  h <- list(
    delta = delta,
    nobj = nobj,
    ndim = ndim,
    snew = snew,
    itel = itel,
    xnew = xnew,
    dmat = dmat,
    labels = labels
  )
```

## Plots

# Examples

## @degruijter_67